\name: A hierarchical Bayesian model for Supernova Cosmology

### 2017-09-20 papers/methods/paper.tex
Tex update
Adding bib and starting paper intro

@@

@@

\section{Simple Model Validation}

Simple

\section{SNANA Validation}

Multisim and bulk

\section{Systematic Strength Test}

Checking that random systematic permutations are less significant than stat

\section{Extension for Photometric SN}

Better outlier pop

@@

\bibliographystyle{mnras}
\bibliography{bib.bib}

@@

\section{Some extra material}

>>>>

Almost two decades have passed since the discovery of the accelerating universe \citep{Riess1998, Perlmutter1999}. Since that time, of the number of observed Type Ia supernovae (SN Ia) have increased by more than an order of magnitude thanks to modern surveys at both low redshift \citep{Bailey2008, Freedman2009, Hicken2009,  Contreras2010, Conley2011}, and higher redshift \citep{Astier2006, Wood-Vasey2007, Balland2009, Amanullah2010}. Cosmological analysis of these supernovae samples \citep{Kowalski2008, Conley2011, Suzuki2012, Betoule2014, Rest2014} have been combined with complimentary probes of large scale structure \citep{Alam2017} and the CMB \citep{Hinshaw2013, PlanckCollaboration2013}, and yet, despite these prodigious efforts, the nature of dark energy remains an unsolved mystery.

In attempts to tease out the nature of dark energy, currently running and planned surveys are once again ramping up their statistical power. The Dark Energy Survey \citep[DES,][]{Bernstein2012, Abbott2016} will be observing thousands of Type Ia supernova, attaining both spectroscopic and photometric confirmation. The Large Synoptic Survey Telescope \citep[LSST,][]{Ivezic2008, LSSTScienceCollaboration2009} will produce scores of thousands of photometrically classified supernovae. Such increased statistical power demands a similarly increased fidelity and flexibility in modelling the supernovae for cosmological purposes, as systematic uncertainty will prove to be the limiting factor in our analyses.

As such, staggering effort is being put into developing more sophisticated supernovae analyses. \citet{Scolnic2016} and \citet{Kessler2017} explore sophisticated simulation corrections to traditional analyses. Approximate Bayesian computation methods also make use of simulations, trading traditional likelihoods and analytic approximations for more robust models with only the cost of increased computational time \citep{Weyant2013, Jennings2016}. Hierarchical Bayesian Models abound \citep{Mandel2009, March2011, March2014a, Rubin2015, Shariff2016, Roberts2017}, however often face difficulties finding sufficient analytic approximations for complicated effects such as Malmquist bias.
\rule{\linewidth}{1pt}

@@

\subsection{General Description}

@@

\subsection{Applied to Spectroscopic Sample}

Minimal outliers

\section{Application to DES}

\subsection{Simulating DES SN data}

\subsection{Results on simulated data (ie projections)}

\subsubsection{Spectroscopic Sample}

\subsubsection{Photometric sample}

\subsection{Comparison with bells and whistles fixed}

\subsection{Model validation}

appoximate\_simple\_test.py

multisim

bulk

\section{Systematics Strength Test}

systematics test

\section{Interesting Implementation Details}

Anything interesting.

Also talk about non-analytic correction factors (and their failure - mc integration, GP, NNGP)

@@

\bibliographystyle{mnras}
\bibliography{bib}

@@

\section{Papers}
